---
title: "Alcohol vs Seat choice"
author: "Taylor Dickie-Mahtesian"
date: "9/14/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row you choose to sit in??

$H_0$: There is no difference in alcohol consumption based on which row one sits.

$H_A$: There is a difference in alcohol consumption based on which row one sits.

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
in the boxplot people who consume more alcohol sit in the back row.There is not much of a difference in alcohol consumption between people who sit in the from and the middle.   
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

the plots above show that people who sit in the back row consume more alcohol than those who sit in the front row and middle row. 

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```

based on the numerical summary the back row sitters consume far more alcohol than both front row sitters and middle row sitters.

## Inferential Tests
   
```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
```{r}
plot(TukeyHSD(model1))
```

the p value is 0.000116 therefor we reject the null hypothesis which is there is no difference in alcohol consumption based on which row one sits.There is a difference in alcohol consumption based on which row one sits.

The tukey test shows that there is no difference between the middle-front row sitters but there is a difference between middle-back row sitters and front-back sitters. 

## Conclusions

In conclusion people who sit in the back row consume more alcohol than both the front sitters and middle sitters, however there is no difference in alcohol consumption between front row sitters and middle row sitters.
